Observations from Parallelising Three Maximum Common (Connected) Subgraph Algorithms

### 2017-06-01 paper/paper.tex
I know my ABCs

\author{Ruth Hoffmann \inst{1} \and Ciaran McCreesh\thanks{This work was supported by the
Engineering and Physical Sciences Research Council [grant numbers EP/K503058/1, EP/M508056/1, and EP/M508056/1]}
\inst{2} \and Patrick Prosser \inst{2} \and Samba Ndojh Ndiaye\thanks{This work
was supported by the ANR project SoLStiCe (ANR-13-BS02-0002-01)} \inst{3}
\and Craig Reilly \samethanks[1] \inst{2}
\and Christine Solnon\samethanks[2]\inst{4} \and James Trimble\samethanks[1] \inst{2}}

>>>>

\author{
    Ruth Hoffmann \inst{1}
    \and Ciaran McCreesh\thanks{This work was supported by the Engineering and Physical Sciences Research Council [grant numbers EP/K503058/1, EP/M508056/1, and EP/M508056/1]} \inst{2}
    \and Samba Ndojh Ndiaye\thanks{This work was supported by the ANR project SoLStiCe (ANR-13-BS02-0002-01)} \inst{3}
    \and Patrick Prosser \inst{2}
    \and Craig Reilly \samethanks[1] \inst{2}
    \and Christine Solnon\samethanks[2]\inst{4} \and James Trimble\samethanks[1] \inst{2}}
